Spatial Reasoning and Statistical Graphics

### 2014-10-30 Paper/Draft1/TestingVisualAptitude.Rnw
Remove unnecessary comments

\section{Methods}
\subsection{Measures of visuospatial ability}
\comment{Use the setup in the lineup protocol section to justify each of the tests chosen. }
\comment{Besides pointing out what we asked participants to do, we also need some why, and also why in particular these tests were selected. part of the validity consideration can go in here - and the classification from the naval test of the tests we picked into different classes (maybe already with a hint that for our data these weren't actually orthogonal classes, because we found a really high correlation between card rotation and paper folding.)\\
}

>>>>

\section{Methods}
\subsection{Measures of visuospatial ability}
